---
title: "&nbsp;"

page_layout: full
title-block-banner: ../images/cover_consulting.JPG
---

# Portfolio

A selection of past projects showcasing my work in data pipelines, R package development, etc. If you'd like to discuss a similar project, feel free to [contact me](../about.qmd).

## Data pipelines & management 🎓


```{r}
#| echo: false
#| message: false
#| warning: false

library(readr)
library(dplyr)
library(knitr)

pipeline <- read_csv("portfolio_pipeline.csv", show_col_types = FALSE)

pipeline %>%
  arrange(desc(start_date)) %>%
  mutate(start_date_parsed = as.Date(paste0(start_date, "-01")),
         start_fmt = format(start_date_parsed, "%b %Y"),
         
         end_date_str = ifelse(is.na(end_date), NA_character_, paste0(end_date, "-01")),
         end_date_parsed = as.Date(end_date_str),
         end_fmt = format(end_date_parsed, "%b %Y"),
         
         Date = if_else(!is.na(end_date_parsed), 
                        paste0(start_fmt, " – ", end_fmt), 
                        paste0(start_fmt, " - Present")),
         
         Details = paste0("**", title, "** <br> ", host, " - ", institution, " <br> ", location)) %>%
  
  select(Date, Details) %>%
  kable(escape = FALSE, 
        col.names = c("", ""))
```



## R package development 📦

-   **birdnetTools** (2025 - present) - **Creater / Maintainer** - R package for post-processing, visualizatino, and validation of BirdNET output. Developed in collaboration with the BirdNET team. Available on GitHub. ([Documentation](https://birdnet-team.github.io/birdnetTools/))

-   **bbsTaiwan** (2024 - present) - **Creater / Maintainer** - R package for accessing and analyzing Taiwan Breeding Bird Survey (BBS) data. Developed for national biodiversity research and public engagement. Available on GitHub. ([Documentation](https://sunnytseng.github.io/bbsTaiwan/))



## Workshop & tutorial 🏫

```{r}
#| echo: false
#| message: false
#| warning: false

library(readr)
library(dplyr)
library(knitr)

workshops <- read_csv("portfolio_workshop.csv", show_col_types = FALSE)

workshops %>%
  arrange(desc(date)) %>%
  mutate(
    start_date_parsed = as.Date(paste0(date, "-01")),
    end_date_str = ifelse(is.na(end_date), NA_character_, paste0(end_date, "-01")),
    end_date_parsed = as.Date(end_date_str),
    start_fmt = format(start_date_parsed, "%b %Y"),
    end_fmt = format(end_date_parsed, "%b %Y"),
    Date = if_else(!is.na(end_date_parsed), paste0(start_fmt, " – ", end_fmt), start_fmt),
    Details = paste0("**", title, "** (", role, ") <br> ", host, " (", institution, ")")) %>%
  select(Date, Details) %>%
  kable(escape = FALSE, 
        col.names = c("", ""))
```


## Code review & troubleshooting 💬

During my PhD at the University of Northern British Columbia, I co-founded the [Applied Analysis Hub (AAH)](https://unbcaah.opened.ca/), a research support group providing one-on-one code review and troubleshooting for students and faculty. This gave me extensive experience reviewing code, particularly for graduate students' research projects.
